Fast, Robust Classification with Applications to Periodic Variable Stars

### 2012-05-09 report/ms.tex
one more small change
added very modest contribution to report ms.tex.

\subsection{The Data Sets}

@@

\subsection{Conclusions}
\begin{enumerate}
\item constructing intervals is non-trivial in many high dimensional problems
\item not clear that this robust framework is ideal when new observation might have low error on certain features
\item kernels, are they possible to use
\end{enumerate}

>>>>

\subsection{The Data Sets}
The first dataset analyzed contained two classes of Cepheids (CEP):  classical and [popII].  Each class consisted of $n=200$ observations and $p=58$ features so that each observation is hyperrectangle in $\mathbb{R}^{58}$. The second dataset consisted of two classes of RR,  RR Lyrae AB and RR Lyrae D, with the same values of $n$ and $p$.
\subsubsection{Preprocessing the data with quantile ranking}
A quantile ranking technique was used to normalize values in each feature dimension by reducing the effects of outliers. Viewing the interval data as a three-dimensional array, the end-slices corresponding to the lower- and upper-bounds of the confidence intervals were isolated and then concatenated together to yield a $2n\times p$ array whose values were then mapped to the standard normal distribution. Features containing all zeroes or some NaNs were removed from the dataset.

@@

\subsubsection{Performance}
The performance of the combined SVM model was compared to those of its degenerates by computing expected losses for multiple values of $\lambda$ and $\rho$.  For a given $(\lambda,\rho)$, the expected loss was computed by performing cross-validation in 90-10 splits so that the union of testing points across splits is the entire dataset and the intersection is disjoint. See surface plots of loss versus $(\lambda,\rho)$: for the CEP dataset, $\lambda\in \lbrace 0\rbrace\cup [0.375,0.750]$ and $\rho\in\lbrace 0\rbrace\cup [0.090,0.032]$ while for the RR dataset, $\lambda\in\lbrace 0\rbrace\cup [54,284]$ and $\rho\in\lbrace 0\rbrace\cup [0.375,0.750]$. Observe that $(\lambda^*,\rho^*)\neq (0,0)$ for both datasets, which implies that the combined model outperforms both of its degenerates. For the CEP dataset, the optimal $(\lambda^*,\rho^*)=(9,0.320)$ yielded 13.25\% classification error while for the RR dataset, $(\lambda^*,\rho^*)=(284,0.48)$ yielded 21.50\% classification error. THESE NUMBERS DON'T LOOK RIGHT, MUST RERUN analyze_feature.m.

The curves of loss versus $\lambda$ and loss versus $\rho$ were also analyzed.  The loss versus $\lambda$ plot corresponds to the standard point SVM model in Hastie while the loss versus $\rho$ plot corresponds to the interval SVM model in El Ghaoui. Observe the convex-like curvatures, which suggest global minima and hence optimal $\lambda$ and $\rho$.

\subsubsection{Feature selection as suggested by $||\beta||_0$ values}

\subsection{Conclusions}
\begin{enumerate}
\item constructing intervals is non-trivial in many high dimensional problems
\item not clear that this robust framework is ideal when new observation might have low error on certain features
\item kernels, are they possible to use
\item links to code / git repo
\end{enumerate}
